Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-07-21 ms.tex
small updates to table

In this paper, we estimate the radio emission from RGHJs and examine the potential to detect planetary them. 
In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission.
\S3 presents an estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
%\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable. 
\S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the offsetting effect of the electrons spiraling down along the planetary magnetic field.
Observability with current and near-future instruments is also examined in \S4. 
Finally, \S5 concludes the paper with a brief summary.

@@

The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}. 
By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
%If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
%We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
%%%
\begin{eqnarray}
r_s 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
&=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius}
\end{eqnarray}
%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htdp]
\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
\begin{center}
\begin{tabular}{c|ccc} \hline \hline\\[-0.5pc]
Instrument & Band & Sensitivity & Time  \\[.25pc]
 &  & $\mu$Jy~hr$^{1/2}$ &  hr \\[0.25pc] 
\hline\\[-0.5pc]
ASKAP & 700-1700~MHz & 37 & 3.4 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
GMRT & 220~MHz &  \\
HERA  & 70~MHz  &  &  \\
LOFAR  & 120~MHz  &  &  \\
LWA  & 70~MHz  &  &  \\
SKA  & 200~MHz  &  &  \\
UTR-2 & & & \\
VLA  & P-band (270-430~MHz)  \\ \hline
\end{tabular}
\end{center}
\label{tab:sens}
\tablecomments{Time estimates to reach 10~$\mu$Jy RMS.  We consider only
telescopes that can reach this in less than XX hours without
being confusion limited.}
\end{table}

>>>>

In this paper, we estimate radio emission from RGHJs and examine the potential to detect planetary them. 
In \S2, we describe our assumptions for stellar wind, planetary magnetosphere, frequency of radio emission, and the scaling of planetary radio emission.
\S3 presents an estimate of the spectral radio intensity of RGHJs and compares them with what might be expected from canonical hot Jupiters.
%\S3 also describes the surprising result that, although the planetary magnetic field is crucial to the generation of radio emission at all, there might be an important region in parameter space in which planets with stronger magnetic fields are less easily observable. 
\S4 discusses possible obstacles to detect radio emission from RGHJs, in particular the effects of intrinsic radio emission of evolved stars and the offsetting effect of the electrons spiraling down along the planetary magnetic field.
Observability with current and near-future instruments is also examined in \S4. 
Finally, \S5 concludes the paper with a brief summary.

@@

The radius of the magnetic stand-off point, $r_s$, is obtained based on the balance between the stellar wind pressure and the planetary magnetic pressure: 
%%%
\begin{equation}
m_p n v ^2 \sim \frac{B^2}{8\pi}\left( \frac{r_s}{R_p} \right)^{-6}  \label{eq:stand-off}
\end{equation}
%%%
The radius obtained for Jupiter from this equality is about a half of actual radius of Magnetosphere \citep[][]{griesmeier2005}. 
By scaling this radius with equations (\ref{eq:n}) and (\ref{eq:stand-off}), the radius of magnetosphere of planets would be estimated as:
%If the radius of magnetosphere is estimated by scaling that of Jupiter according to equations (\ref{eq:n}) and (\ref{eq:stand-off}), 
%We estimate $r_s$ simply by scaling Jovian magnetosphere \citep[$r_{s,\,J} \sim 84 R_J$;][]{joy2002} according to equation (\ref{eq:stand-off}), i.e., 
%%%
\begin{eqnarray}
\nonumber r_s 
%&\sim & R_p \left( \frac{B^2}{8\pi m_{\rm p}nv^2} \right)^{1/6}  \\
&=& r_{s,\,J} \left( \frac{B}{10~\mbox{G}} \right)^{1/3} \left( \frac{a}{5.2\mbox{AU}} \right)^{1/3}  \\
&& \times \left( \frac{\dot M_\star}{\dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{v_{\odot }} \right)^{-1/6} \\
\nonumber &=& 11.3 \, R_J \left( \frac{B}{10~\mbox{G}} \right)^{1/3}  \left( \frac{a}{5\mbox{AU}} \right)^{1/3} \\
&& \times \left( \frac{\dot M_\star}{10^6 \dot M_\odot} \right)^{-1/6}  \left( \frac{\dot v}{10^{-1}v_{\odot }} \right)^{-1/6}
 \label{eq:stand-off-radius}
\end{eqnarray}
%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htdp]
\caption{Detectability of Hot Jupiters with Current and Future Radio Telescopes.}
\begin{center}
\begin{tabular}{c|ccccc} \hline \hline\\[-0.5pc]
Instrument & Band & Sensitivity & Time  & Resolution & Confusion limit\\[.25pc]
 &  & $\mu$Jy~hr$^{1/2}$ &  hr & \arcsec\ & $\mu$Jy \\[0.25pc] 
\hline\\[-0.5pc]
%ASKAP & 700-1700~MHz & 37 & 342.3 \\ % table 3 of http://www.atnf.csiro.au/projects/askap/config.html
GMRT  & 235~MHz &  165.6 & 6860 & 13 \\ % http://gmrt.ncra.tifr.res.in/~astrosupp/obs_setup/sensitivity.html
HERA  & 70~MHz  &  &  \\ % http://reionization.org/wp-content/uploads/2015/05/HERA0_imaging.pdf
% https://www.astron.nl/~heald/test/sens.php; 
% 24 core stations, 16 remote, 8 international, 488 subbands
LOFAR & ~45~MHz  &  833!! &  &  & \\
LOFAR & ~60~MHz  &  648!! &  &  & \\
LOFAR & 120~MHz  &  51.73 &  &  & \\  
LOFAR & 150~MHz  &  40.97 &  &  & \\  
LWA   & ~70~MHz  &  &  \\
SKA   & 200~MHz  &  &  \\
UTR-2 & & & \\
VLA P-band & (270-470~MHz)  & 138  & 4760 & \\
\hline
\end{tabular}
\end{center}
\label{tab:sens}
\tablecomments{Time estimates to reach 2~$\mu$Jy RMS.  We consider only
telescopes that can reach this in less than XX hours without
being confusion limited.}
\end{table*}
